Process-based phenotypes: an application to the ontology of cell physiology

### 2011-11-28 paper/drinking.tex
added captions

\author[Hoehndorf et al.]{Robert Hoehndorf$^1$ and Midori
  A. Harris$^3$ and Heinrich Herre(?) and Gabriella Rustici$^2$ and
  Georgios V. Gkoutos$^{1}$}

\address{$^{1}$Department of Genetics, University of Cambridge,
  Downing Street, Cambridge, Cambridge CB2 3EH, UK\\
  $^{2}$EBI, Wellcome Trust Genome Campus, Hinxton, Cambridge,
  Cambridge CB10 1SD, UK\\
  $^{3}$Department of Biochemistry; University of Cambridge, 80 Tennis
  Court Road, Cambridge CB2 1GA, UK}

@@

\subsection{Processes and their participants}
\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{onto.pdf}
  \caption{Overview over ...\label{fig:onto}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=.5\textwidth]{processpatterns.pdf}
  \caption{Overview over ...\label{fig:patterns}}
\end{figure}

>>>>

\author[Hoehndorf et al.]{Robert Hoehndorf$^1$ and Midori
  A. Harris$^2$ and Heinrich Herre$^3$ and Gabriella Rustici$^4$ and
  Georgios V. Gkoutos$^{1}$}

\address{$^{1}$Department of Genetics, University of Cambridge,
  Downing Street, Cambridge, Cambridge CB2 3EH, UK\\
  $^{2}$Department of Biochemistry; University of Cambridge, 80 Tennis
  Court Road, Cambridge CB2 1GA, UK\\
  $^{3}$Institute for Medical Informatics, Statistics and
  Epidemiology, University of Leipzig, Haertelstrasse 16-18, 04107
  Leipzig, Germany\\
  $^{4}$EBI, Wellcome Trust Genome Campus, Hinxton, Cambridge,
  Cambridge CB10 1SD, UK
}

@@

\subsection{Processes and their participants}
\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{onto.pdf}
  \caption{Overview over basic top-level categories. Physical objects
    are entities that are wholly present at time points. Qualities are
    attributes of entities. Functions are capabilities that arise from
    physical objects with their qualities, and processes are
    temporally extended entities that may be realizations of a
    function.\label{fig:onto}}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=.5\textwidth]{processpatterns.pdf}

  \caption{\label{fig:patterns}Six examples of processes with
    non-comparative and comparative process attributes.  We assume
    that the processes labelled $a$, $b$, $c$ and $d$ are all
    instances of the class of processes $P$.  On the left side, three
    regulation (of $P$) processes are illustrated which exhibit
    non-comparative attributes. The first process has an attribute of
    {\em rhythmic} occurrence of $P$ because the instances of $P$ are
    temporally equidistantly distributed. The second example shows an
    {\em arrhythmic} occurrence of $P$, and the third examples shows
    an {\em increasing frequency} (of $P$). A regulation process with
    an increasing frequency (of $P$) is a process in which the
    frequency of occurrences of $P$ is lower in the first half of the
    process than in the second...}
\end{figure}
